---
title: "RC_analysis"
author: "Sara Perrins"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
final <- read.csv("~/Desktop/R Projects/RC/Combined.df.final.csv")
require(dplyr)
```
### Recovery Capital  
Histogram shows non normal distribution
```{r analysis_Create Recovery Capital variable}

final$RecoveryCapital <-NA
final$RecoveryCapital <- rowSums(final[ c("Q15_1","Q15_2","Q15_3","Q15_4","Q15_5","Q15_6","Q15_7","Q15_8","Q15_9","Q15_10","Q15_11")]) 

summary(final$RecoveryCapital)
hist(final$RecoveryCapital) #Shows non-normal distribution
```

### Results: Sample Characteristics- Treatment versus Control

**N = 22 Treatment; N = 18 Control**
```{r results_sample characteristics_groups}
Results_SampleCharacteristics_TreatmentControl <- final %>%
  filter(Q5 !="") %>%
  group_by(TreatmentControl) %>%
  summarise(N = n())
print(Results_SampleCharacteristics_TreatmentControl)

```
### Results: Sample Characteristics - N by grantee

```{r results_sample characteristics_grantee}
Results_SampleCharacteristics_grantee <- final %>%
  filter(Q5 !="") %>%
  group_by(TreatmentControl, Organization) %>%
  summarise(N = n())
print(Results_SampleCharacteristics_grantee)
```
### Results: Sample Characteristics - Sex  

Table below shows n and percent of each sex category by Treatment vs Control;  
Codebook: 1	Male (including transgender);  
2	Female (including transgender);  
3	Non-binary/ non-conforming;  
4	Prefer to self describe (fill-in);  
5	Prefer not to say

``` {r results_sample characteristics_sex}

Results_SampleCharacteristics_Sex <- final %>%
  filter(!is.na(Q5)) %>%
  group_by(TreatmentControl) %>% 
  count(QID17) %>%
    mutate(prop = n / sum(n))

print(Results_SampleCharacteristics_Sex)
```
### Results: Sample Characteristics - Race 

Table below shows n and percent of each race category by Treatment vs Control;  
Codebook: 
1	White  
2	Black or African American  
3	American Indian or Alaska Native  
4	Asian or Pacific Islander  
5	Other (fill-in)  
6	Don't know  
7	Prefer not to say. 
```{r results_sample characteristics_race}
Results_SampleCharacteristics_Race <- final %>%
  filter(!is.na(Q5)) %>%
  group_by(TreatmentControl) %>% 
  count(Q21) %>%
    mutate(prop = n / sum(n))
print(Results_SampleCharacteristics_Race)
```
Control: 42.1 White; 
Treatment: 68.2% White
  
    
    
### Results: Sample Characteristics - Ethnicity

Table below shows n and percent of each ethnicity category by Treatment vs Control;  
Codebook: "Are you of Hispanic, Latino/a, or Spanish origin?"  
1	Yes  
2	No. 
3	Don't know. 
4	Prefer not to say  

```{r results_sample characteristics_ethnicity}
Results_SampleCharacteristics_Ethnicity <- final %>%
  filter(!is.na(Q5)) %>%
  group_by(TreatmentControl) %>% 
  count(Q23) %>%
    mutate(prop = n / sum(n))
print(Results_SampleCharacteristics_Ethnicity)


```
Control: 
15.8% Hispanic, Latino/a, or Spanish origin; 
63.2% NOT Hispanic, Latino/a, or Spanish origin  

Treatment:  
86.3% NOT Hispanic, Latino/a, or Spanish origin

### Results: Sample Characteristics - Education
Codebook: "What is the highest grade or year of school you completed?"  
1	Never attended school or only kindergarten  
2	Elementary   
3	Some high school  
4	High school graduate or equivalent  
5	Some college or technical school  
6	College graduate  
7	Prefer not to say  

```{r results_sample characteristics_education}
Results_SampleCharacteristics_Education <- final %>%
  filter(!is.na(Q5)) %>%
  group_by(TreatmentControl) %>% 
  count(Q25) %>%
    mutate(prop = n / sum(n))
print(Results_SampleCharacteristics_Education)
```

### Reframing to count those with high school education or higher:

```{r results_sample characteristics_Education_HS}
Results_SampleCharacteristics_Education.MinimumHighSchool <- final %>%
  filter(!is.na(Q5)) %>%
  group_by(TreatmentControl) %>% 
  count(Q25 > 3 & Q25 < 7) %>%
    mutate(prop = n / sum(n))
print(Results_SampleCharacteristics_Education.MinimumHighSchool)
```
Control:  
42.1% Have not had a high school education  
52.6%$ Have a high school education or higher. 
Treatment: 
81.8% Have a high school education or higher  


### Results_Recovery Capital: mean, min, max and sd for entire treatment/control groups

Shows spread and center for outcome: Recovery Capital by treatment group:  

```{r results_recovery capital_descriptive}
Results_SampleCharacteristics_RecoveryCapital <- final %>%
  filter(!is.na(Q5)) %>%
  group_by(TreatmentControl) %>% 
  summarise(meanRecoveryCapital = mean(RecoveryCapital, na.rm = T), sdRecoveryCapital = sd(RecoveryCapital, na.rm = T), minRecoveryCapital = min(RecoveryCapital, na.rm = T), maxRecoveryCapital = max(RecoveryCapital, na.rm = T)) %>% 
  ungroup()
print(Results_SampleCharacteristics_RecoveryCapital)

```

#### Results_Recovery Capital: Mean, Median and SD for each item by treatment group. 
Results suggest the Treatment group have higher mean scores for each of the 11 items.  
Some median numbers are same across groups, but several are higher for the treatment group.  

``` {r results_RecoveryCapital_Itemized_MeanSD}
Results_RecoveryCapital_Itemized <- final %>%
  filter(!is.na(Q5)) %>%
  group_by(TreatmentControl) %>% 
  summarise_at(.vars = names(.)[24:34],
               .funs = c(Median = "median", Mean = "mean", SD = "sd"), na.rm = T)
  
print(Results_RecoveryCapital_Itemized)

```

#### Results_Recovery Capital: Mann-Whitney test results for TOTAL Recovery Capital

This non parametric test assess whether the treatment and control groups are identical in their total RC score (i.e., the sum of their responses to Q15_1:Q15_11) 
Results suggest that the treatment and control groups are NOT statistically different in their median scores.  
W = 146.5, p-value = 0.2354. 

```{r Results_Recovery Capital: Mann-Whitney tests}

test.RecoveryCapital <- wilcox.test(RecoveryCapital ~ TreatmentControl, data=final) 
print(test.RecoveryCapital)
```
#### Results_Recovery Capital: Statistical Test for Differences for Each Item  

Results suggest marginal significance (p = 0.073) for item 4;  
marginal significance (p = 0.072) for item 9;  
marginal significance (p = 0.057) for item 11.  

```{r Results_Recovery Capital_Mann Whitney U Test}
require(tidyverse)
map_df(final[c(24:34)], ~ wilcox.test(.x ~ TreatmentControl, data = final, na.rm = TRUE)$p.value)
```

