---
title: "RC_analysis"
author: "Sara Perrins"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
final <- read.csv("~/Desktop/R Projects/RC/Combined.df.final.csv")
require(dplyr)
```
### Recovery Capital  
Histogram shows non normal distribution
```{r analysis_Create Recovery Capital variable}

final$RecoveryCapital <-NA
final$RecoveryCapital <- rowSums(final[ c("Q15_1","Q15_2","Q15_3","Q15_4","Q15_5","Q15_6","Q15_7","Q15_8","Q15_9","Q15_10","Q15_11")]) 

summary(final$RecoveryCapital)
hist(final$RecoveryCapital) #Shows non-normal distribution
```

### Results: Sample Characteristics- Treatment versus Control

**N = 22 Treatment; N = 18 Control**
```{r results_sample characteristics_groups}
Results_SampleCharacteristics_TreatmentControl <- final %>%
  filter(Q5 !="") %>%
  group_by(TreatmentControl) %>%
  summarise(N = n())
print(Results_SampleCharacteristics_TreatmentControl)

```

### Results: Sample Characteristics - Sex  

Table below shows n and percent of each sex category by Treatment vs Control;  
Codebook: 1	Male (including transgender);  
2	Female (including transgender);  
3	Non-binary/ non-conforming;  
4	Prefer to self describe (fill-in);  
5	Prefer not to say

``` {r results_sample characteristics_sex}

Results_SampleCharacteristics_Sex <- final %>%
  filter(!is.na(Q5)) %>%
  group_by(TreatmentControl) %>% 
  count(QID17) %>%
    mutate(prop = n / sum(n))

print(Results_SampleCharacteristics_Sex)
```
### Results: Sample Characteristics - Race 

Table below shows n and percent of each sex category by Treatment vs Control;  
Codebook: 
1	White  
2	Black or African American  
3	American Indian or Alaska Native  
4	Asian or Pacific Islander  
5	Other (fill-in)  
6	Don't know  
7	Prefer not to say. 
```{r results_sample characteristics_race}
Results_SampleCharacteristics_Race <- final %>%
  filter(!is.na(Q5)) %>%
  group_by(TreatmentControl) %>% 
  count(Q21) %>%
    mutate(prop = n / sum(n))
print(Results_SampleCharacteristics_Race)
```
Control: 42.1 White; 
Treatment: 68.2% White
  
    
    
### Results: Sample Characteristics - Ethnicity

Table below shows n and percent of each ethnicity category by Treatment vs Control;  
Codebook: "Are you of Hispanic, Latino/a, or Spanish origin?"  
1	Yes  
2	No. 
3	Don't know. 
4	Prefer not to say  

```{r results_sample characteristics_ethnicity}
Results_SampleCharacteristics_Ethnicity <- final %>%
  filter(!is.na(Q5)) %>%
  group_by(TreatmentControl) %>% 
  count(Q23) %>%
    mutate(prop = n / sum(n))
print(Results_SampleCharacteristics_Ethnicity)


```
Control: 
15.8% Hispanic, Latino/a, or Spanish origin; 
63.2% NOT Hispanic, Latino/a, or Spanish origin  

Treatment:  
86.3% NOT Hispanic, Latino/a, or Spanish origin

### Results: Sample Characteristics - Education
Codebook: "What is the highest grade or year of school you completed?"  
1	Never attended school or only kindergarten  
2	Elementary   
3	Some high school  
4	High school graduate or equivalent  
5	Some college or technical school  
6	College graduate  
7	Prefer not to say  

```{r results_sample characteristics_ethnicity}
Results_SampleCharacteristics_Education <- final %>%
  filter(!is.na(Q5)) %>%
  group_by(TreatmentControl) %>% 
  count(Q25) %>%
    mutate(prop = n / sum(n))
print(Results_SampleCharacteristics_Education)
```

Reframing to count those with high school education or higher:

```{r results_sample characteristics_ethnicity}
Results_SampleCharacteristics_Education.MinimumHighSchool <- final %>%
  filter(!is.na(Q5)) %>%
  group_by(TreatmentControl) %>% 
  count(Q25 > 3 & Q25 < 7) %>%
    mutate(prop = n / sum(n))
print(Results_SampleCharacteristics_Education.MinimumHighSchool)
```
Control:  
42.1% Have not had a high school education  
52.6%$ Have a high school education or higher. 
Treatment: 
81.8% Have a high school education or higher  


